A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-08-29 rr-flow.Rmd
fixed broken author note

authornote: This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompaniying Github repository:  To comment on our paper, please add an issue to the Github repository of our paper: <https://github.com/aaronpeikert/reproducible-research/>.  To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the Github repository of our paper: <https://github.com/aaronpeikert/reproducible-research/issues>.

>>>>

authornote: This paper is fully reproducible using the workflow described in this paper. All materials can be found on the accompaniying Github repository <https://github.com/aaronpeikert/reproducible-research/>.  To provide feedback or any other type of comment or questions regarding our workflow, please add an issue to the Github repository of our paper [https://github.com/aaronpeikert/reproducible-research/issues](https://github.com/aaronpeikert/reproducible-research/issues).
